Cover Letter: Cudele (Paper 306)

### 2018-01-09 paper/sections/1_introduction.tex
paper: final revision for round 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client}\footnote{In this paper, ``client"
is a storage client or application that interacts with the metadata server,
``administrator" is a system administrator that configures the storage, and
``end-users" interact with the file system via home directories or runtimes.  }
is unreasonable. This problem is exacerbated by current hardware and software
trends: parallel runtimes like Hadoop and Spark use storage systems to
implement important scheduling and timing semantics and  \oldcomment{; for
example, } HPC architectures are transitioning from complex storage stacks with
burst buffer, file system, object store, and tape tiers to more simplified
stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put pressure on
data access because more requests from different nodes end up hitting the same
layers in parallel\oldcomment{and latencies cannot be hidden while data
migrates across tiers}.

@@

% What did we do
%\footnote{HDFS itself is not directly evaluated in this paper, although the
%semantics and their performance is explored in~\S\ref{sec:use-case-1}.} 
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The BatchFS and RAMDisk subtrees are decoupled from the global
namespace and have similar consistency/durability behavior to those systems;
the HDFS subtree has weaker than strong consistency because it lets clients
read files opened for writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which
means that not all updates are immediately seen by all clients; and the POSIX
IO subtree retains the rigidity of POSIX IO's strong consistency.  Subtrees
without policies inherit the consistency/durability semantics of the parent and
future work will examine embeddable or inheritable policies.

>>>>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client}\footnote{In this paper, ``client"
is a storage client or application that interacts with the metadata server,
``administrator" is a system administrator that configures the storage, and
``end-users" interact with the file system via home directories or runtimes.  }
is unreasonable. This problem is exacerbated by current hardware and software
trends; for example,  HPC architectures are transitioning from complex storage
stacks with burst buffer, file system, object store, and tape tiers to more
simplified stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put pressure on
data access because more requests from different nodes end up hitting the same
software layers in parallel and latencies cannot be hidden while data migrates
across tiers.

@@

% What did we do
%\footnote{HDFS itself is not directly evaluated in this paper, although the
%semantics and their performance is explored in~\S\ref{sec:use-case-1}.} 
To address this problem, we present an API and framework that lets administrators
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The BatchFS and RAMDisk subtrees are decoupled from the global
namespace and have similar consistency/durability behavior to those systems;
the HDFS subtree has weaker than strong consistency because it lets clients
read files opened for writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which
means that not all updates are immediately seen by all clients; and the POSIX
IO subtree retains the rigidity of POSIX IO's strong consistency.  Subtrees
without policies inherit the consistency/durability semantics of the parent and
future work will examine embeddable or inheritable policies.
